Verifying Demonstrations

### 2017-09-15 abstract.tex
Fixes warnings from Syntastic
Starts to adapt to PoPETS format

% What's the problem?
Say Alice organizes a protest against the current regime leader Eve.
The protest is held in some location(s) and Alice wants to estimate the number 
of participants to prove a certain support to her cause.
% Why is it a problem?
Current methods have wide margins for error.
In addition, Alice may be tempted to cheat by estimating the number of 
participants as high as possible whereas the government's incentive is to make 
this estimation as low as possible to support Eve.

@@

\keywords{%
  crowd counting;
  protesting;
  electronic voting;
  location proof;
  privacy
}

>>>>

% What's the problem?
Say Alice organizes a protest against the current regime leader Eve.
The protest is held in some location (or locations) and Alice wants to estimate 
the number of participants to prove a certain support to her cause.
% Why is it a problem?
Current methods have wide margins for error.
In addition, Alice may be tempted to cheat by estimating the number of 
participants as high as possible whereas the government's incentive is to make 
this estimation as low as possible to support Eve.

@@
